---
title: "FragPipe-Analyst report"
date: "`r format(Sys.time(), '%d %B, %Y')`"
params:
  data: NA
  alpha: NA
  lfc: NA
  normalization: NA
  imputation: NA
  fdr_correction: NA
  num_signif: NA
  tested_contrasts: NA
  numbers_input: NA
  coverage_input: NA
  pca_input: NA
  correlation_input: NA
  detect_input: NA
  density_input: NA
  p_hist_input: NA
  heatmap_input: NA
  missval_input: NA
  dep: NA
  cvs_input: NA
  volcano_input: NA
output: 
  pdf_document:
    extra_dependencies: ["float"]
    fig_caption: yes
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(opts.label="kill_prefix", fig.pos = "!H", out.extra = "")
# Remove line number and Comment "##" from printing
```

## Method details

The raw data files were analyzed using FragPipe to obtain peptide identifications and their respective label-free quantification values using IonQuant. Statistical analysis was performed based on the combined_peptide.tsv file. First, contaminants were filtered out. In addition, peptides that were not identified/quantified consistantly in same condition have been removed (). The quantification values were converted to log2 scale if intensities were used. A normalization was then applied (`params$normalizaition`).  Samples were grouped by conditions and missing values were imputed using the `params$imputation`. Peptide-wise linear models combined with empirical Bayes statistics were used for the differential expression analyses. The _limma_ package from R Bioconductor was used to generate a list of differentially expressed peptides for each pair-wise comparison. A cutoff of the _adjusted p-value_ of `r params$alpha` (`params$fdr_correction` method) along with a |log2 fold change| of `r params$lfc` has been applied to determine differentially expressed peptides in each pairwise comparison.


### Quick summary of parameters used:

* Normalization = <span style="color:blue">`r params$normalization`</span>
* Imputation = <span style="color:blue">`r params$imputation`</span>
* Tested comparisons = <span style="color:blue">`r params$tested_contrasts`</span>
* Adjusted _p-value_ cutoff <= <span style="color:blue">`r params$alpha`</span>
* Log2 fold change cutoff >= <span style="color:blue">`r params$lfc`</span>

## Results

### FragPipe result output contains `r nrow(params$data)` peptides of which _`r nrow(params$dep())`_ peptides were reproducibly quantified.

### `r params$num_signif` peptides differ significantly between samples.

\pagebreak



## Exploratory Analysis (QC Plots)

### Principle Component Analysis (PCA) plot


```{r pca_plot, echo=FALSE, fig.height= 4}
print(params$pca_input())
```
\pagebreak

### Sample Correlation matrix

```{r correlation_heatmap, echo=FALSE, fig.keep='last', tidy=T, out.height='50%'}
print(params$correlation_input())
```
\pagebreak

### Sample Coefficient of variation (CVs)

```{r sample_cv,  echo=FALSE, warning=FALSE }
print(params$cvs_input())
```
\pagebreak

### Proteomics Experiment Summary

Peptides quantified per sample (after pre-processing).

```{r numbers, echo=FALSE, warning=FALSE, results='hide', message=FALSE }
print(params$numbers_input())
```
\pagebreak

Peptide overlap in all samples.


```{r coverage, echo=FALSE, warning=FALSE}
print(params$coverage_input())
```
\pagebreak



## Missing Value handling

### Missing value distribution
Peptides' expression distribution before and after imputation. The plot showing the effect of imputation on peptide expression distribution.

```{r imputation_effect, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
print(params$density_input())
```
\pagebreak

## Differential Expression Analysis (Results Plots) 

### Heatmap
  A plot representing an overview of expression of all significant (differentially expressed) peptides (rows) in all samples (columns).

 
```{r heatmap_2,  echo=F, warning=F, error=T, results='hide', fig.keep="first"}
print(params$heatmap_input())
```

### Volcano Plots

```{r volcano,  echo=FALSE, warning=FALSE, comment=NA}
# print(params$volcano_input())
# source("./R/volcano_function.R", local = knitr::knit_global())
for(i in params$tested_contrasts){
 print(plot_volcano_customized(params$dep(),contrast = i,label_size = 2, add_names = F))
}
```






