---
title: "FragPipe-Analyst report"
date: "`r format(Sys.time(), '%d %B, %Y')`"
params:
  data: NA
  alpha: NA
  lfc: NA
  num_signif: NA
  tested_contrasts: NA
  numbers_input: NA
  coverage_input: NA
  pca_input: NA
  correlation_input: NA
  missval_input: NA
  detect_input: NA
  density_input: NA
  p_hist_input: NA
  heatmap_input: NA
  dep: NA
  pg_width: NA
  cvs_input: NA
  volcano_input: NA
output: 
  pdf_document:
    fig_caption: yes
always_allow_html: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(opts.label="kill_prefix") # Remove line number and Comment "##" from printing
```

## Method details

The raw data files were analyzed using TMT workflows in FragPipe to obtain protein quantification. 

Statistical analysis was performed using an in-house generated R script based on the ProteinGroup.txt file. Protein-wise linear models combined with empirical Bayes statistics were used for the differential expression analyses. The _limma_ package from R Bioconductor was used to generate a list of differentially expressed proteins for each pair-wise comparison. A cutoff of the _adjusted p-value_ of 0.05 (Benjamini-Hochberg method) along with a |log2 fold change| of 1 has been applied to determine significantly regulated proteins in each pairwise comparison.


### Quick summary of parameters used:

* Tested pairwise comparisons = <span style="color:blue">`r params$tested_contrasts`</span>  
* Adjusted _p-value_ cutoff <= <span style="color:blue">`r params$alpha`</span>  
* Log fold change cutoff >= <span style="color:blue">`r params$lfc`</span>  

## Results

#### MaxQuant result output contains `r nrow(params$data)` proteins groups of which _`r nrow(params$dep())`_ proteins were reproducibly quantified.

#### `r params$num_signif` proteins differ significantly between samples.

\pagebreak



## Exploratory Analysis (QC Plots)

#### Principle Component Analysis (PCA) plot


```{r pca_plot, echo=FALSE, fig.height= 4}
print(params$pca_input())
```
\pagebreak

#### Sample Correlation matrix

```{r correlation_heatmap, echo=FALSE, fig.keep='first'}
print(params$correlation_input())
```
\pagebreak

#### Sample Coefficient of variation (CVs)

```{r sample_cv,  echo=FALSE, warning=FALSE }
print(params$cvs_input())
```
\pagebreak

### Proteomics Experiment Summary

Protein quantified per sample (after pre-processing).

```{r numbers, echo=FALSE, warning=FALSE, results='hide', message=FALSE }
print(params$numbers_input())
```
\pagebreak

Protein overlap in all samples.


```{r coverage, echo=FALSE, warning=FALSE}
print(params$coverage_input())
```
\pagebreak



## Missing Value handling

#### Missing value heatmap
A heatmap for proteins with missing value in each dataset. Each row represent a protein with missing value in one or more replicate. Each replicate is clustered based on presence of missing values in the sample. 


```{r missing_value_heatmap, echo=FALSE, message=FALSE, results='hide',warning=FALSE, fig.keep='first', tidy=TRUE}
params$missval_input()
```
\pagebreak

#### Missing value distribution
Protein expression distribution before and after imputation. The plot showing the effect of imputation on protein expression distribution.

```{r imputation_effect, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
print(params$density_input())
```
\pagebreak

## Differential Expression Analysis (Results Plots) 

#### Heatmap
  A plot representing an overview of expression of all significant (differentially expressed) proteins (rows) in all samples (columns).

 
```{r heatmap_2,  echo=F, warning=F, error=T, results='hide', fig.keep="first"}
print(params$heatmap_input())
```

#### Volcano Plots

```{r volcano,  echo=FALSE, warning=FALSE, comment=NA}
print(params$volcano_input())
# source("./R/volcano_function.R", local = knitr::knit_global())
#for(i in params$tested_contrasts){
#  # print(paste0('volcano_plot_',i,sep=""))
#  print(plot_volcano_new(params$dep(),contrast = i,label_size = 2, add_names = F))
# }
```






